Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-27 appendix.Rmd
Fix typos in appendix

CRQ analyses for sextiled Phoenix event data found increased levels of coupling between positive events and social cohesion, irrespective of target or source and target filtering. Negative events were not coupled with social cohesion irrepective of filtering.

@@

CRQ analyses for sextiled ICEWS event data found coupling between both positive and negative events with social cohesion, irrespective of target or source and target filtering. Negative events were more stongly coupled with social cohesion than positive events for the target only analyses.
The abscence of coupling between negative events and social cohesion in the Phoenix CRQ analyses speaks to the unreliability of event data, and that nonlinear analyses in general are only as valuable as the quality of the data being used.

>>>>

CRQ analyses for sextiled Phoenix event data found increased levels of coupling between positive events and social cohesion, irrespective of target or source and target filtering. Negative events were not coupled with social cohesion irrespective of filtering.

@@

CRQ analyses for sextiled ICEWS event data found coupling between both positive and negative events with social cohesion, irrespective of target or source and target filtering. Negative events were more strongly coupled with social cohesion than positive events for the target only analyses.
The absence of coupling between negative events and social cohesion in the Phoenix CRQ analyses speaks to the unreliability of event data, and that nonlinear analyses in general are only as valuable as the quality of the data being used.

### 2020-05-27 appendix.tex
Fix syntax
Fix typos in appendix

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for target only Phoenix data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endhead
DET & 31.065 & 0.246 & & 38.955 & 0.000 & *** & 31.854 & 0.130
&\tabularnewline
NRLINE & 144.000 & 0.220 & & 174.000 & 0.000 & *** & 148.000 & 0.106
&\tabularnewline
maxL & 4.000 & 0.456 & & 5.000 & 0.082 & . & 4.000 & 0.461
&\tabularnewline
L & 2.188 & 0.555 & & 2.270 & 0.030 & * & 2.182 & 0.637 &\tabularnewline
ENTR & 0.513 & 0.527 & & 0.650 & 0.027 & * & 0.504 & 0.615
&\tabularnewline
rENTR & 0.467 & 0.273 & & 0.469 & 0.264 & & 0.459 & 0.344
&\tabularnewline
LAM & 32.051 & 0.290 & & 46.154 & 0.007 & ** & 30.769 & 0.333
&\tabularnewline
TT & 2.273 & 0.211 & & 2.400 & 0.071 & . & 2.400 & 0.073 &
.\tabularnewline
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for source and target Phoenix
data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endhead
DET & 31.558 & 0.168 & & 37.377 & 0.000 & *** & 25.740 & 0.984
&\tabularnewline
NRLINE & 145.000 & 0.172 & & 169.000 & 0.000 & *** & 119.000 & 0.983
&\tabularnewline
maxL & 4.000 & 0.437 & & 5.000 & 0.088 & . & 4.000 & 0.440
&\tabularnewline
L & 2.207 & 0.355 & & 2.243 & 0.125 & & 2.193 & 0.500 &\tabularnewline
ENTR & 0.547 & 0.334 & & 0.610 & 0.100 & . & 0.521 & 0.494
&\tabularnewline
rENTR & 0.498 & 0.164 & & 0.440 & 0.411 & & 0.474 & 0.261
&\tabularnewline
LAM & 38.462 & 0.079 & . & 48.718 & 0.001 & *** & 21.795 & 0.798
&\tabularnewline
TT & 2.500 & 0.021 & * & 2.235 & 0.294 & & 2.429 & 0.042 &
*\tabularnewline
\bottomrule
\end{longtable}

CRQ analyses for sextiled Phoenix event data found increased levels of
coupling between positive events and social cohesion, irrespective of
target or source and target filtering. Negative events were not coupled
with social cohesion irrepective of filtering.

@@

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for target only ICEWS data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endhead
DET & 39.250 & 0.000 & *** & 37.870 & 0.000 & *** & 38.659 & 0.000 &
***\tabularnewline
NRLINE & 177.000 & 0.000 & *** & 169.000 & 0.001 & *** & 170.000 & 0.001
& ***\tabularnewline
maxL & 5.000 & 0.074 & . & 5.000 & 0.099 & . & 5.000 & 0.101
&\tabularnewline
L & 2.249 & 0.089 & . & 2.272 & 0.045 & * & 2.306 & 0.009 &
**\tabularnewline
ENTR & 0.619 & 0.080 & . & 0.653 & 0.040 & * & 0.705 & 0.007 &
**\tabularnewline
rENTR & 0.447 & 0.362 & & 0.471 & 0.246 & & 0.509 & 0.125
&\tabularnewline
LAM & 43.590 & 0.017 & * & 39.744 & 0.051 & . & 42.308 & 0.028 &
*\tabularnewline
TT & 2.267 & 0.222 & & 2.385 & 0.093 & . & 2.357 & 0.111
&\tabularnewline
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for source and target ICEWS data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endhead
DET & 34.122 & 0.011 & * & 37.771 & 0.000 & *** & 39.448 & 0.000 &
***\tabularnewline
NRLINE & 152.000 & 0.037 & * & 168.000 & 0.000 & *** & 173.000 & 0.000 &
***\tabularnewline
maxL & 5.000 & 0.090 & . & 5.000 & 0.081 & . & 7.000 & 0.005 &
**\tabularnewline
L & 2.276 & 0.026 & * & 2.280 & 0.024 & * & 2.312 & 0.002 &
**\tabularnewline
ENTR & 0.663 & 0.021 & * & 0.661 & 0.021 & * & 0.698 & 0.005 &
**\tabularnewline
rENTR & 0.478 & 0.236 & & 0.477 & 0.233 & & 0.434 & 0.459
&\tabularnewline
LAM & 34.615 & 0.186 & & 39.744 & 0.045 & * & 48.718 & 0.003 &
**\tabularnewline
TT & 2.250 & 0.236 & & 2.385 & 0.077 & . & 2.235 & 0.267
&\tabularnewline
\bottomrule
\end{longtable}

CRQ analyses for sextiled ICEWS event data found coupling between both
positive and negative events with social cohesion, irrespective of
target or source and target filtering. Negative events were more stongly
coupled with social cohesion than positive events for the target only
analyses. The abscence of coupling between negative events and social
cohesion in the Phoenix CRQ analyses speaks to the unreliability of
event data, and that nonlinear analyses in general are only as valuable
as the quality of the data being used.

>>>>

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for target only Phoenix data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endhead
DET & 31.065 & 0.241 & & 38.955 & 0.000 & *** & 31.854 & 0.139
&\tabularnewline
NRLINE & 144.000 & 0.229 & & 174.000 & 0.000 & *** & 148.000 & 0.105
&\tabularnewline
maxL & 4.000 & 0.421 & & 5.000 & 0.087 & . & 4.000 & 0.452
&\tabularnewline
L & 2.188 & 0.544 & & 2.270 & 0.039 & * & 2.182 & 0.580 &\tabularnewline
ENTR & 0.513 & 0.526 & & 0.650 & 0.033 & * & 0.504 & 0.550
&\tabularnewline
rENTR & 0.467 & 0.290 & & 0.469 & 0.276 & & 0.459 & 0.310
&\tabularnewline
LAM & 32.051 & 0.284 & & 46.154 & 0.008 & ** & 30.769 & 0.314
&\tabularnewline
TT & 2.273 & 0.196 & & 2.400 & 0.072 & . & 2.400 & 0.063 &
.\tabularnewline
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for source and target Phoenix
data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endhead
DET & 31.558 & 0.178 & & 37.377 & 0.000 & *** & 25.740 & 0.988
&\tabularnewline
NRLINE & 145.000 & 0.189 & & 169.000 & 0.000 & *** & 119.000 & 0.989
&\tabularnewline
maxL & 4.000 & 0.467 & & 5.000 & 0.084 & . & 4.000 & 0.454
&\tabularnewline
L & 2.207 & 0.368 & & 2.243 & 0.123 & & 2.193 & 0.509 &\tabularnewline
ENTR & 0.547 & 0.343 & & 0.610 & 0.104 & & 0.521 & 0.492
&\tabularnewline
rENTR & 0.498 & 0.135 & & 0.440 & 0.432 & & 0.474 & 0.244
&\tabularnewline
LAM & 38.462 & 0.073 & . & 48.718 & 0.000 & *** & 21.795 & 0.790
&\tabularnewline
TT & 2.500 & 0.017 & * & 2.235 & 0.280 & & 2.429 & 0.048 &
*\tabularnewline
\bottomrule
\end{longtable}

CRQ analyses for sextiled Phoenix event data found increased levels of
coupling between positive events and social cohesion, irrespective of
target or source and target filtering. Negative events were not coupled
with social cohesion irrespective of filtering.

@@

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for target only ICEWS data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endhead
DET & 39.250 & 0.000 & *** & 37.870 & 0.000 & *** & 38.659 & 0.000 &
***\tabularnewline
NRLINE & 177.000 & 0.000 & *** & 169.000 & 0.000 & *** & 170.000 & 0.000
& ***\tabularnewline
maxL & 5.000 & 0.093 & . & 5.000 & 0.081 & . & 5.000 & 0.087 &
.\tabularnewline
L & 2.249 & 0.089 & . & 2.272 & 0.033 & * & 2.306 & 0.009 &
**\tabularnewline
ENTR & 0.619 & 0.074 & . & 0.653 & 0.030 & * & 0.705 & 0.008 &
**\tabularnewline
rENTR & 0.447 & 0.368 & & 0.471 & 0.261 & & 0.509 & 0.118
&\tabularnewline
LAM & 43.590 & 0.013 & * & 39.744 & 0.047 & * & 42.308 & 0.030 &
*\tabularnewline
TT & 2.267 & 0.208 & & 2.385 & 0.065 & . & 2.357 & 0.092 &
.\tabularnewline
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for source and target ICEWS data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative
events & p & sig.\tabularnewline
\midrule
\endhead
DET & 34.122 & 0.014 & * & 37.771 & 0.000 & *** & 39.448 & 0.000 &
***\tabularnewline
NRLINE & 152.000 & 0.064 & . & 168.000 & 0.000 & *** & 173.000 & 0.000 &
***\tabularnewline
maxL & 5.000 & 0.092 & . & 5.000 & 0.093 & . & 7.000 & 0.002 &
**\tabularnewline
L & 2.276 & 0.030 & * & 2.280 & 0.024 & * & 2.312 & 0.003 &
**\tabularnewline
ENTR & 0.663 & 0.022 & * & 0.661 & 0.022 & * & 0.698 & 0.005 &
**\tabularnewline
rENTR & 0.478 & 0.211 & & 0.477 & 0.242 & & 0.434 & 0.475
&\tabularnewline
LAM & 34.615 & 0.178 & & 39.744 & 0.047 & * & 48.718 & 0.002 &
**\tabularnewline
TT & 2.250 & 0.233 & & 2.385 & 0.067 & . & 2.235 & 0.295
&\tabularnewline
\bottomrule
\end{longtable}

CRQ analyses for sextiled ICEWS event data found coupling between both
positive and negative events with social cohesion, irrespective of
target or source and target filtering. Negative events were more
strongly coupled with social cohesion than positive events for the
target only analyses. The absence of coupling between negative events
and social cohesion in the Phoenix CRQ analyses speaks to the
unreliability of event data, and that nonlinear analyses in general are
only as valuable as the quality of the data being used.
